A systematic search for transiting planets using \KT

### 2015-02-11 ms.tex
a few words about false positives

In \KT, we will not be able to rely on any of these techniques to
characterize systems \textit{en masse}.
There are typically only a handful of transits, meaning differences
between ``odd'' and ``even'' transits must be large to create
a significant difference.
Searching for ellipsoidal varaitions is hindered by the short time
baseline and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently
than in the original \kepler\ mission.
In that data, centroid positions are measured for the data during and out of
transit by coadding all the relevant frames in each quarter.
Such a technique is feasible due to the remarkably stable pointing of the
instrument.
Searching for centroid variations with this method is more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
With \KT\ this is only possible if one understands the pointing of the
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.

>>>>

In \KT, the precision of these tests is lower and they must be applied with
care.
There are typically only a handful of transits, meaning differences between
``odd'' and ``even'' transits must be large to create a significant
difference.
Searching for ellipsoidal varaitions is hindered by the short time baseline
and the increased photometric uncertainty in \KT\ data.
Centroid variations are feasible in \KT\ but must be treated differently than
in the original \kepler\ mission where this effect was generally measured
using difference imaging (cite Howell).

To obtain an initial assessment of the astrophysical false positive rate in
our catalog of planet candidates, we test for centroid offsets and variable
depth transits using the machinery that we have already established for
modeling the systematic trends in the data.
This is only the first word and a more complete characterization of our
catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in prep).

To measure \emph{centroid offsets}, we start by empirically measuring the
pixel centroid time series for each candidate by modeling the pixels near the
peak as a two-dimensional quadratic and finding the maximum at each time.
This method has been shown to produce higher precision centroid measurements
than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
in prep?).
Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
SOMECANDIDATE.
Much like the photometry, this signal is dominated by the rigid body motion
of the spacecraft and we can, in fact, model it identically.
Previously (SOMEEQUATION), we modeled the light curve as a linear combination
of ELCs and a simple box transit model at a given period, phase, and duration.
Under this model, the maximum likelihood depth can be computed analytically.
If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
that we compute becomes the centroid motion in transit in units of pixels.

In that data, centroid positions are measured for the data during and out of
transit by coadding all the relevant frames in each quarter.
Such a technique is feasible due to the remarkably stable pointing of the
instrument.
Searching for centroid variations with this method is more difficult in \KT:
to measure a centroid offset, one must know where the centroid is
supposed to be.
With \KT\ this is only possible if one understands the pointing of the
spacecraft at a specific time.
In theory, this is possible: the spacecraft is a rigid body, and by measuring
the mean motion of stars across the detector over time, the
Euler angles can be inferred at all times.
However, properly measuring positions of stars is a difficult problem:
the centroid depends sensitively on the (unknown) flat field, which must
be simultaneously inferred.
